tesis

### 2020-07-30 production/prod_analisis.rmd
desarrollo teorico

@@

```{r}
screenreg(list(results_1,results_2,results_3, results_6), type="text")
```

>>>>

```{r}
library(ggplot2)
library(ggplot2)
library(hrbrthemes)
#install.packages("hrbrthemes")
data$alto_nse<-as.character(ifelse(data$nse>=0,1,0))

scatter <-ggplot(data, aes(x=p.civ, y=p.leng, color=alto_nse)) + 
    geom_point(size=2) +
    theme_classic()

@@

```{r}
results_12 = lmer(p.civ ~ 1 + Libros +  Ocupacion + ip_estudiante +  ip_padres + Educacion + m_nse +  (1 | idschool), data = data, REML=F)

screenreg(list(results_1,results_12, results_2,results_3, results_6), type="text")
```
